Spatial evolution of solar wind discontinuities in the outer heliosphere

### 2024-09-21 article.qmd
update: bib format

In this study, we present a statistical analysis of discontinuities observed from Earth’s orbit to Jupiter, utilizing data collected by the Juno spacecraft during its cruise phases (2011-2016) ([[@boltonJunoMission2017]]). The primary goal of this paper is to investigate the radial dependence of the occurrence rate and other properties of discontinuities, in order to gain insights into their evolution and origin. Continuous measurements at 1 AU from missions such as Wind, ARTEMIS, and STEREO have been utilized to distinguish temporal effects from spatial variations by examining the characteristics of discontinuities at two radial distances simultaneously. This distinction is crucial because temporal variations could easily be misinterpreted as spatial variations ([[@tsurutaniInterplanetaryDiscontinuitiesTemporal1979]]). Due to the potential misidentification of the normal direction of the magnetic field when using the minimum variance analysis (MVA) method [@hausmanDeterminingNatureOrientation2004; @liuFailuresMinimumVariance2023], we do not differentiate between the types of discontinuities, whether they are tangential, rotational, or either [@neugebauerReexaminationRotationalTangential1984].

Previous studies on the radial dependencies of solar wind discontinuities have been conducted by several authors (e.g., [[@marianiVariationsOccurrenceRate1973]]; [[@tsurutaniInterplanetaryDiscontinuitiesTemporal1979]]; [[@sodingRadialLatitudinalDependencies2001]]). However, the data used in these studies were rarely obtained in conjunction with measurements at fixed radial distances, and the methods employed to identify discontinuities were not robust for situations involving weak magnetic fields and long durations encountered at large radial distances. Additionally, some measurements at different radial distances were significantly separated in time, with limited time ranges covered ([[@sodingRadialLatitudinalDependencies2001]]). Consequently, there remains ambiguity in interpreting the results of these studies.

>>>>

In this study, we present a statistical analysis of discontinuities observed from Earth’s orbit to Jupiter, utilizing data collected by the Juno spacecraft during its cruise phases (2011-2016) [@boltonJunoMission2017]. The primary goal of this paper is to investigate the radial dependence of the occurrence rate and other properties of discontinuities, in order to gain insights into their evolution and origin. Continuous measurements at 1 AU from missions such as Wind, ARTEMIS, and STEREO have been utilized to distinguish temporal effects from spatial variations by examining the characteristics of discontinuities at two radial distances simultaneously. This distinction is crucial because temporal variations could easily be misinterpreted as spatial variations [@tsurutaniInterplanetaryDiscontinuitiesTemporal1979]. Due to the potential misidentification of the normal direction of the magnetic field when using the minimum variance analysis (MVA) method [@hausmanDeterminingNatureOrientation2004; @liuFailuresMinimumVariance2023], we do not differentiate between the types of discontinuities, whether they are tangential, rotational, or either [@neugebauerReexaminationRotationalTangential1984].

Previous studies on the radial dependencies of solar wind discontinuities have been conducted by several authors [e.g., @marianiVariationsOccurrenceRate1973; @tsurutaniInterplanetaryDiscontinuitiesTemporal1979; @sodingRadialLatitudinalDependencies2001]. However, the data used in these studies were rarely obtained in conjunction with measurements at fixed radial distances, and the methods employed to identify discontinuities were not robust for situations involving weak magnetic fields and long durations encountered at large radial distances. Additionally, some measurements at different radial distances were significantly separated in time, with limited time ranges covered [@sodingRadialLatitudinalDependencies2001]. Consequently, there remains ambiguity in interpreting the results of these studies.
